---
title: "R Markdown turtorial - SW Carpentry"
author: "Christoffer M. Kramer"
date: "21/10/2020"
output: html_document
---

**This is bold**

 _this is italics_

* and - can create lists

- this 
- is
* A
* list

"1." "2." etc. creates numbered lists, you can also use the same number

1. this 
1. is 
1. a 
1. list 

"#" creates titles "##" creates subtitles etc.
#Title
##Subtitle
###Subsubtitle

[this is a hyperlink](http://swcarpentry.github.io/r-novice-gapminder/15-knitr-markdown/index.html)
[This is a picture of me drinking af beer](IMG_3335.JPG)

Use dollar sign for math equations 
$1+1 = 3 (or is it 2?)

For help with formatting look at "Markdown Qucik reference" under help

Always give code chunks a unique name
```{r test}
library(ggplot2)
library(gapminder)

gapminder
theme_set(theme_bw())  # set theme to white background for better visibility
anim <- ggplot(subset(gapminder, continent == "Asia"), aes(gdpPercap, lifeExp)) +
  geom_point()

anim

```

You can change how chunks are displayed

- echo=FALSE to avoid having the code itself shown.
- Use results="hide" to avoid having any results printed.
- Use eval=FALSE to have the code shown but not evaluated.
- Use warning=FALSE and message=FALSE to hide any warnings or messages produced.
- Use fig.height and fig.width to control the size of the figures produced (in inches).

use global_options to set options for alle code chunks
below is a very small point graph

```{r test2, fig.height = 1, fig.widt = 2}
anim
```
YOu can make inline codes, which replaces the code with the value of the result

`r round(2, 2)`



